Index measures for oak decline severity using phenotypic descriptors

### 2019-12-14 manuscript/manuscript.Rmd
fixed descriptor importance plots

The phenotypic descriptors were analysed using 100 repetitions of unsupervised random forest using the randomForest R package v`r packageVersion('randomForest') %>% as.character()` [@liaw2002].
The proximity matrices from each repetition were averaged to a single proximity matrix ($P$).
This was then transformed to a dissimilarity matrix ($1 - P$) and scaled to two dimensions using  multidimensional scaling (MDS).
The first MDS dimension ($D$) was first inverted ($1 - D$) to ensure the correct dimension orientation relative to decline severity.
It was then min-max scaled to give a scale between 0 and 1 with more severely declining trees having a score closer to 1.
This dimension was named the PDI.
The second MDS dimension was similarly inverted to ensure the correct dimension orientation relative to decline type.
The dimension was then min-max scaled and then transformed ($2D - 1$) to give a scale between -1 and 1 with COD trees having a score closer to -1 and AOD having a score closer to 1. 
This dimension was named the DAI.
With different data, it is likely that the MDS dimensions may require inversion prior to min-max scaling to ensure their correct orientation.

>>>>

The phenotypic descriptors were analysed using 100 repetitions of unsupervised random forest using the randomForest R package v`r packageVersion('randomForest') %>% as.character()` [@liaw2002].
The proximity matrices from each repetition were averaged to a single proximity matrix ($P$).
This was then transformed to a dissimilarity matrix ($1 - P$) and scaled to two dimensions using  multidimensional scaling (MDS).
The first MDS dimension ($D$) was first inverted ($1 - D$) to ensure the correct dimension orientation relative to decline severity.
It was then min-max scaled to give a scale between 0 and 1 with more severely declining trees having a score closer to 1.
This dimension was named the PDI.
The second MDS dimension was min-max scaled and then transformed ($2D - 1$) to give a scale between -1 and 1 with COD trees having a score closer to -1 and AOD having a score closer to 1. 
This dimension was named the DAI.
With different data, it is likely that the MDS dimensions may require inversion prior to min-max scaling to ensure their correct orientation.
